Aggregated Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-10-23 aggregation/agg-objective.tex
More tweaks

In the context of this paper, an ``LCA Study'' should be understood as any aggregation of data under consideration, from a single-operation unit process to a full ISO-style product LCA.  The practice of reporting the results of an LCA study implies the existence of two parties with different information: the study author has full knowledge of the product system model; and the Reader only has knowledge of what the author has disclosed.  Obviously, the level of detail of the disclosure will determine how useful it is to the Reader.  In this context, the reader will want to know the answers to various questions about the model, which we will call \emph{review objectives}.  
At the same time the author may be limited in what she can disclose, which we will call \emph{disclosure constraints}.  The purpose of the framework is to give form to the disclosure so that the requirements of various review objectives, and restrictions associated with various disclosure contraints, can be evaluated clearly.

>>>>

In the context of this paper, an ``LCA Study'' should be understood as any aggregation of data under consideration, from a single-operation unit process to a full ISO-style product LCA.  The practice of reporting the results of an LCA study implies the existence of two parties with different information: the study author has full knowledge of the product system model; and the Reader only has knowledge of what the author has disclosed.  Obviously, the level of detail of the disclosure will determine how useful it is to the Reader.  In this context, the reader will want to know the answers to various review objectives.  
At the same time the author may have constraints that limit what she can disclose.  The purpose of the framework is to give form to the disclosure so that the requirements of various review objectives, and restrictions associated with various disclosure contraints, can be evaluated clearly.
